\mytitle

### 2023-06-06 generated/saved-files.tex
Revisions getting closer to sending to Computer Journal, and renaming the repo
Preparing to upload to Computer Journal

allGitRepos.sh & Shell script generated to download all available 10 GitHub repositories\\
assessments.tex & Main summary table for Supplementary Material\\
clone-date.tex & Running the download script also saves the download dates of GitHub clones\\
constants.tex & Generated \LaTeX\  definitions and constants\\
data-check.html & Convenient list of data sources with DOIs in HTML (enables checking of data just by clicking on HTML links)\\
data.csv & All data from \texttt{data.js} expressed in CSV for convenience\\
example-data.tex & \LaTeX\  example of JSON data\\
flagData.nb & Flags expressed as Mathematica code (facilitates ML or other analysis)\\
legend.tex & Legend for the main assessment table\\
open-doi.sh & Shell script to conveniently open all DOIs\\
page-lengths.tex & Page lengths and totals for Git data, and total pages of papers\\
saved-files.tex & This table of files generated by \texttt{data.js}\\
summary-table.tex & Short summary table\\
supplementary-references.tex & Reference list for Supplementary Material\\

>>>>

% Generated by programs/data.js
allGitRepos.sh & Shell script generated to download all available 10 GitHub repositories\\
assessments.tex & Main summary table for Supplementary Material\\
clone-date.tex & Running the download script also saves the download dates of GitHub clones\\
constants.tex & Generated \LaTeX\  definitions and constants\\
data-check.html & Convenient list of data sources with DOIs in HTML (enables checking of data just by clicking on HTML links)\\
data.csv & All data from \texttt{data.js} expressed in CSV for convenience\\
example-data.tex & \LaTeX\  example of JSON data\\
flagData.nb & Flags expressed as Mathematica code (facilitates ML or other analysis)\\
legend.tex & Legend for the main assessment table\\
open-doi.sh & Shell script to conveniently open all DOIs\\
page-lengths.tex & Page lengths and totals for Git data, and total pages of papers\\
saved-files.tex & This table of files generated by \texttt{data.js}\\
summary-table.tex & Short summary table\\
survey-references.bbl & Reference list for Supplementary Material (bbl file)\\

### 2023-06-06 generated/summary-table.tex
Revisions getting closer to sending to Computer Journal, and renaming the repo
Preparing to upload to Computer Journal

\begin{tabular}{|rrrc|}\hline
Number of papers sampled relying on code&32&100\%&\\\hline\hline
\multicolumn{4}{|l|}{\textbf{Access to code}}\\
Some or all code available&12&38\%&\\
Some or all code in principle available on request&8&25\%&\\
Requested code actually made available (within 2 years 8 months${}^{\star}$)&0&0\%& \\\hline
 \multicolumn{4}{|l|}{{\textbf{Evidence of any software engineering practice}}}\\
Evidence program designed rigorously&{0}&{0\%}&\\
Evidence source code properly tested&{0}&{0\%}&\\
Evidence of any tool-based development&{0}&{0\%}&\\
Team or open source based development&{0}&{0\%}&\\
Other methods, e.g., independent coding methods&{1}&{3\%}&\\\hline
\multicolumn{4}{|l|}{\textbf{Documentation and comments}}\\
Substantial code documentation and comments&2&6\%&\\
Comments explain some code intent&3&9\%&\\
Procedural comments (e.g., author, date, copyright)&10&31\%&\\
No usable comments&17&53\%&\\\hline
\multicolumn{4}{|l|}{\textbf{Repository use}}\\
Used code repository (e.g., GitHub)&9&28\%&\\
Used data repository (e.g., Dryad or GitHub)&9&28\%&\\
Empty repository&1&3\%&\\\hline
\multicolumn{4}{|l|}{{\textbf{Evidence of documented processes}}}\\
Evidence of RAP/\RAPstar\ or any other principles in use to support scrutiny&{0}&{0\%}&\\\hline
\multicolumn{4}{|l|}{\textbf{Adherence to journal code policy (if any)}}\\
Papers published in journals with code policies&26&81\%&\\
Clear breaches of journal code policy (if any) & 11&42\%&(\emph{N}~=~26)\\
\hline\end{tabular}\\
\vskip 1ex ${}^{\star}$Time of 2 years 8 months is wait between code request and date of generating this table.

>>>>

% Generated by programs/data.js
\begin{tabular}{|rrrc|}\hline
Number of papers sampled relying on code&32&100\%&\\\hline\hline
\multicolumn{4}{|l|}{\textbf{Access to code}}\\
Some or all code available&12&38\%&\\
Some or all code in principle available on request&8&25\%&\\
Requested code actually made available (within 2 years 11 months${}^{\star}$)&0&0\%& \\\hline
 \multicolumn{4}{|l|}{{\textbf{Evidence of any software engineering practice}}}\\
Evidence program designed rigorously&{0}&{0\%}&\\
Evidence source code properly tested&{0}&{0\%}&\\
Evidence of any tool-based development&{0}&{0\%}&\\
Team or open source based development&{0}&{0\%}&\\
Other methods, e.g., independent coding methods&{1}&{3\%}&\\\hline
\multicolumn{4}{|l|}{\textbf{Documentation and comments}}\\
Substantial code documentation and comments&2&6\%&\\
Comments explain some code intent&3&9\%&\\
Procedural comments (e.g., author, date, copyright)&10&31\%&\\
No usable comments&17&53\%&\\\hline
\multicolumn{4}{|l|}{\textbf{Repository use}}\\
Used code repository (e.g., GitHub)&9&28\%&\\
Used data repository (e.g., Dryad or GitHub)&9&28\%&\\
Empty repository&1&3\%&\\\hline
\multicolumn{4}{|l|}{{\textbf{Evidence of documented processes}}}\\
Evidence of RAP/\RAPstar\ or any other principles in use to support scrutiny&{0}&{0\%}&\\\hline
\multicolumn{4}{|l|}{\textbf{Adherence to journal code policy (if any)}}\\
Papers published in journals with code policies&26&81\%&\\
Clear breaches of journal code policy (if any) & 11&42\%&(\emph{N}~=~26)\\
\hline\end{tabular}\\
\vskip 1ex ${}^{\star}$Time of 2 years 11 months is wait between code request and date of generating this table.
